---
title: "Correlation and regression analysis example"
output: 
  html_document: 
    theme: paper
    toc: yes
    toc_float: yes
  html_notebook: 
    toc: yes
    toc_float: yes
---

# Problem

Load the data set **cats** from the "MASS" library, which contains information on various anatomical features of house cats.

```{r catsdata}
library(MASS)
data(cats)
```

"Bwt" is the body weight in kilograms, "Hwt" is the heart weight in grams, and "Sex" should be obvious. There are no missing values in any of the variables.

* Have a look at the data set.
* Plot a data (scatterplot of Bwt and Hwt)
* Are "Bwt" and "Hwt" correlated? Test for correlation - use the Pearson correlation coefficient.
* Does "Hwt" depends on "Bwt"? Plot the regression line and then use appropriate plots to check for model assumptions.
* Comment on the diagnostic plots.

# Solution

```{r}
head(cats)
str(cats)
plot(cats$Bwt, cats$Hwt)
plot(cats$Hwt ~ cats$Bwt)
plot(Hwt ~ Bwt, data = cats)
plot(Bwt ~ Hwt, data = cats)
```
```{r}
cor(cats$Bwt, cats$Hwt)
```

```{r}
cor.test(cats$Bwt, cats$Hwt)
```

```{r}
cor.test(cats$Hwt, cats$Bwt)
```

```{r}
mod <- lm(Hwt ~ Bwt, data=cats)
summary(mod)
```
```{r}
plot(cats$Bwt, cats$Hwt)
abline(coef(mod), col="red")
```

```{r}
par(mfrow=c(2,2))
plot(mod)

par(mfrow=c(1,4))
plot(mod)

par(mfrow=c(1,1))
plot(mod)
```











